Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-07-17 prop_letter.tex
prop_iop.tex \subsection{Classical and Quantum Probability Measures} Updating...
small

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Fuzzy Measurements}
 \label{sec:fuzzy}
A \emph{probability space} is a mathematical abstraction specifying
the necessary conditions for reasoning coherently about collections of
uncertain events\nb\cite{Kolmogorov1950,544199,Griffiths2003,Grabisch2016}. In the quantum case, the
events of interest are specified by \emph{projection operators}
$P$. These include the empty projection\nb$\mathbb{0}$, the identity
projection\nb$\mathbb{1}$, projections of the form $\proj{\psi}$ where
$\ket{\psi}$ is a pure quantum state (an element of a Hilbert space),
sums of \emph{orthogonal} projections $P_0$ and $P_1$ with
$P_0P_1=\mathbb{0}$, and products of \emph{commuting} projections
$P_0$ and $P_1$ with $P_0P_1=P_1P_0$. In a well-defined quantum
probability
space\nb\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
each event $P_{i}$ is mapped to a probability\nb$\mu(P_{i})$ using
a probability measure\nb$\mu:\events\rightarrow[0,1]$, where $\events$
is the set of all projections on a given Hilbert space. We impose
the following constraints: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
$\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$, and for each pair
of \emph{orthogonal} projections $P_{0}$ and $P_{1}$, standard probability
measures obey
\begin{equation}
{\mu}\left(P_{0}+P_{1}\right)={\mu}\left(P_{0}\right)+{\mu}\left(P_{1}\right)\,.\label{eq:QuantumProbability-Addition}
\end{equation}

@@

We now have the necessary ingredients to define QIVPMs as a
generalization of both classical IVPMs and conventional quantum
probability measures. We will assume that the quantum IVPM will reduce to
the classical IVPM when the space of quantum events is restricted to
mutually commuting sub-events.

@@

It is now not difficult to verify that for any totally mixed
state\nb$\rho$ on a three-dimensional Hilbert space,
$\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$ is a
QIVPM. Furthemore, we have:
\begin{itemize}
\item If $\left\Vert \rho-\rho'\right\Vert \le1/\left(12n\right)$,
$\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.
\item If $\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
then $\left\Vert \rho-\rho'\right\Vert \le1/n$.
\end{itemize}
In other words, for the states consistent with this QIVPM,
$\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$ will become closer and
closer to $\rho'$ as $n$ goes to infinity. In the limiting case when
the intervals are infinitely precise, i.e.,
$\set{\left[x,x\right]}{x\in\left[0,1\right]}$, any QIVPM can be
recast as a real-valued one and will have a unique state consistent
with it on every projector when $d\ge3$.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Fuzzy Measurements}
 \label{sec:fuzzy}
A \emph{probability space} is a mathematical abstraction specifying
the necessary conditions for reasoning coherently about collections of
uncertain events\nb\cite{Kolmogorov1950,544199,Griffiths2003,Grabisch2016}. In the quantum case, the
events of interest are specified by \emph{projection operators}
$P$. These include the empty projection\nb$\mathbb{0}$, the identity
projection\nb$\mathbb{1}$, projections of the form $\proj{\psi}$ where
$\ket{\psi}$ is a pure quantum state (an element of a Hilbert space),
sums of \emph{orthogonal} projections $P_0$ and $P_1$ with
$P_0P_1=\mathbb{0}$, and products of \emph{commuting} projections
$P_0$ and $P_1$ with $P_0P_1=P_1P_0$. In a well-defined quantum
probability
space\nb\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
each event $P_{i}$ is mapped to a probability\nb$\mu(P_{i})$ using
a probability measure\nb$\mu:\events\rightarrow[0,1]$, where $\events$
is the set of all projections on a given Hilbert space, subject to
the following constraints: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
$\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$, and for each pair
of \emph{orthogonal} projections $P_{0}$ and $P_{1}$:
\begin{equation}
{\mu}\left(P_{0}+P_{1}\right)={\mu}\left(P_{0}\right)+{\mu}\left(P_{1}\right)\,.\label{eq:QuantumProbability-Addition}
\end{equation}

@@

We now have the necessary ingredients to define QIVPMs as a
generalization of both classical IVPMs and conventional quantum
probability measures. We will show that the quantum IVPM will reduce to
the classical IVPM when the space of quantum events is restricted to
mutually commuting sub-events.

@@

It is now not difficult to verify that for any totally mixed
state\nb$\rho$ on a three-dimensional Hilbert space,
$\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$ is a
QIVPM. Furthermore, we have:
\begin{itemize}
\item If $\left\Vert \rho-\rho'\right\Vert \le1/\left(12n\right)$,
$\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.
\item If $\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
then $\left\Vert \rho-\rho'\right\Vert \le1/n$.
\end{itemize}
In other words, for the states consistent with this QIVPM,
$\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$ will become closer and
closer to $\rho'$ as $n$ goes to infinity. In the limiting case when
the intervals are infinitely precise, i.e.,
$\set{\left[x,x\right]}{x\in\left[0,1\right]}$, any QIVPM can be
recast as a real-valued one and will have a unique state consistent
with it on every projector when $d\ge3$.
